---
title: "ADA Midterm"
author: "Courtney Shaw"
date: "10/14/2022"
output: html_document
---

## Question 3 
Using the titanic dataset located at "https://github.com/kijohnson/Data",  prepare an R markdown file that shows the code for a) importing the dataset, b) determining the median age for by passenger class, and c) a plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class. Report the medians by passenger class and upload a PDF or picture of your plot.

## A) Import Dataset and clean code 
```{r}
#open library 
pacman::p_load(tidyverse, table1)

#gridExtra, knitr, kableExtra, mosaic, xtable, pscl, multcomp, pander, MASS, , lmtest, readr, stargazer, sandwich, lmtest, SMPracticals, writexl, broom
```

```{r}
#import data 
titanic_df <- read_csv("https://raw.githubusercontent.com/kijohnson/Data/main/titanic.csv")
```

```{r}
#view titantic dataset 
view(titanic_df)
summary(titanic_df)
```

```{r}
#recode Pclass variable as factor 
titanic_df_clean <- titanic_df %>%
  mutate(Pclass = factor(Pclass, levels = c(1: 3), labels = c("Class 1", "Class 2", "Class 3")))
```

## B) Determine median age by passenger class  
```{r}
#create table to determine median age by passenger class 
table1(~ Age | Pclass, data = titanic_df_clean)
```
Median age by passenger class: 
Class 1 = 38.5 
Class 2 = 29.0
Class 3 = 24.0  


## C) Plot that shows medians, spread of data, and outliers for the continuous variable age according to passenger class
```{r}
#creat boxplot for Pclass and Age 
ggplot(titanic_df_clean, aes(x = Pclass, y = Age)) + 
  geom_boxplot(aes(fill = Pclass)) + 
  labs(x = "Passenger Class", y = "Age", title = "Titantic Passenger Class by Age") + 
  scale_fill_brewer(palette = "Dark2", guide = guide_legend(reverse = TRUE))
```


